---
title: "RBootcampExercise1Module3"
author: "LG dePillis"
date: "May 30, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) #echo=TRUE means when you knit the rmarkdown, these lines will be printed

require(hflights) # We need hflights package - if this library isn't here, then install the package automatically
library(hflights) # Include library in setup
library(ggplot2)  # Include library in setup
```

### Subsetting (subsampling) and Plotting

### (1) Subsampling


```{r subsampling}
hflightsSub <- hflights[sample(1:nrow(hflights), 10000, replace = FALSE), ] # take 10000 samples
```

### (2-1) Plot a histogram (using base graphics)

Plot a histogram of the flight delays with negative delays set to zero, censoring delay times at a maximum of 60 minutes:

```{r histogram, echo=FALSE}
hflightsSub$DepDelay[hflightsSub$DepDelay < 0] <- 0
hflightsSub$DepDelay[hflightsSub$DepDelay > 60] <- 60
hist(hflightsSub$DepDelay)
```

### (2-2) Plot a histogram (using ggplot2)

Use of `geom="histogram"`:

```{r ggplothist, echo=TRUE, message=FALSE, warning=FALSE}
p <- qplot(hflightsSub$DepDelay, geom="histogram") 
p
```

### (3) Plot the arrival delay against the departure delay as a scatterplot. And give it a main title and axis labels.

```{r scatterplot, echo=TRUE}
# Keep only Delay data that are not NA

ggp <- ggplot(hflights, (aes(ArrDelay, DepDelay))) + (geom_point()) 
# ggp 
ggp + labs(x = "Arrival Delay", y = "Departure Delay", title = "Scatterplot of Arrival Delay vs Departure Delay")
```

```{r scatterplot2, echo=TRUE}
### Alternate
plot(hflightsSub$ArrDelay, 
     hflightsSub$DepDelay, 
     main = "Arival vs Departure Delay",
     xlab = "Arrival Delay",
     ylab = "Departure Delay")


### Plot using plot only instead of ggplot, and see the difference

```

## R Markdown